Abstract Spatial Specification of Stencil Computations

### 2016-06-24 paper.tex
Remove multi-set related things, add some of the proofs
clean whitespace
explanation of mapping regions to syntax

\begin{definition}The product of two models $\otimes$ is defined:
%%
\begin{align*}
M \otimes N & =
  \{(u \bowtie v)_i \mid i \in \{0, \ldots, 2^n \}, (u, v) \in
              M \times N\}^1
\end{align*}
The $\bowtie$ operation, which we call \emph{pairwise permutation}
(described below), constructs a $2^n \times n$ matrix ($2^n$-vector of
$n$-vectors).  Using this, the $\otimes$ operation constructs the set
of every pairwise permutation for every pair $(u, v)$ of $n$-vectors in the
Cartesian product of $M \times N$.

@@

Given the set $\textsf{regions}(M)$ of spans covering the indexing
space, the next step converts these into abstract syntax tree
for the specification language.

>>>>

\begin{definition}The product of two models $\otimes$ is defined:
%%
\begin{align*}
M \otimes N & =
  \{(u \bowtie v)_i \mid i \in \{0, \ldots, 2^n \}, (u, v) \in
              M \times N\}
\end{align*}
The $\bowtie$ operation, which we call \emph{pairwise permutation}
(described below), constructs a $2^n \times n$ matrix ($2^n$-vector of
$n$-vectors).  Using this, the $\otimes$ operation constructs the set
of every pairwise permutation for every pair $(u, v)$ of $n$-vectors in the
Cartesian product of $M \times N$.

@@

Given the set $\textsf{regions}(M)$ of spans covering the indexing
space, the next step converts these into abstract syntax trees 
for the specification language.

For each span $S = [\vect{l} \; \vect{u}]$, 
for each dimension, each pair of entries in the lower- and upper-bound 
vectors is mapped to a concrete \textit{spec}, as defined by the
$\mathsf{conv}$ function: 
%%
\begin{align*}
& \mathsf{conv}_i\; [\vect{l} \; \vect{u}] = \\
& \begin{cases}
%% FWD
 \stenFwd{\vect{u}_i}{i}  & \vect{l}_i = 0 \; \wedge \; \vect{u}_i > 0 \\[0.7em]
 \texttt{irreflexive(dims=$i$)}, & \\
 \qquad \stenFwd{\vect{u}_i}{i}  & \vect{l}_i = 1 \; \wedge \; \vect{u}_i > 0 \\[0.7em]
%% BWD
 \stenBwd{|\vect{l}_i|}{i}  & \vect{l}_i < 0 \; \wedge \; \vect{u}_i = 0 \\[0.7em]
 \texttt{irreflexive(dims=$i$)}, & \\
 \quad\;\; \stenBwd{|\vect{l}_i|}{i}  & \vect{l}_i < 0 \; \wedge \; \vect{u}_i = -1 \\[0.7em]
%% CEN
 \stenCen{\vect{u}_i}{i}  &\vect{l}_i < 0 \; \wedge \; \vect{u}_i > 0
 \; \\
 & \qquad\quad \wedge \; |\vect{l}_i| = \vect{u}_i \\[0.7em]
 \stenBwd{|\vect{l}_i|}{i} & \vect{l}_i < 0 \; \wedge \; \vect{u}_i >
 0 \\
\quad \texttt{+} \; \stenFwd{\vect{u}_i}{i}  & \qquad\quad \wedge \; |\vect{l}_i| \neq \vect{u}_i \\[0.7em]
% ABSOLUTE REP
 \texttt{irreflexive(dims=$i$)} & \vect{l}_i = \infty \; \vee \; \vect{u}_i
 = \infty \\[0.7em]
% BOUND
 \texttt{atMost}, \stenFwd{\vect{u}_i}{i} & \vect{l}_i > 1 \\[0.7em]
 \texttt{atMost}, \stenBwd{|\vect{l}_i|}{i} \quad & \vect{l}_i < (-1) \\[0.7em]
  \end{cases}
\end{align*}
%%
The first two cases map to \texttt{forward} stencils since the lower
bound is $0$ or $1$, with the depth determined by the upper bound of
the span. If the lower bound is $1$, then the 
$0$-offset point is missing so the specification is given an
\texttt{irreflexive} modifier. The second two cases are similar for
\texttt{backward} but now the depth of the region is determined by the
absolute of the lower bound. In the fifth-case, when the lower bound
is negative and the upper bound is positive and they have the same
magnitude, then a \texttt{centered} region is constructed with
the depth as the common magnitude. If the magnitudes are not the same
(sixth case) then separated \texttt{forward} and \texttt{backward}
regions are summed, with their corresponding depths.

In the case where either bound is $\infty$, representing a non
neighbourhood index, then a simple \texttt{irreflexive} specification
is given with no regions, indicating that there is not even reflexive
0-offset access in this dimension.

Finally in the last two cases, if the lower bound is greater than 1 
(which implies the upper bound is greater than 1 too) then 
this represents a region that is not at the origin (or next to) the
origin and thus not representable in the specificaiton language. 
Thus, an upper bound is instead returned showing the maximum extent
of the region. The last case is the dual, when the lower bound is less
than $-1$, giving an upper bound on a \texttt{backward} specification.

\begin{lemma}
$\mathsf{conv}_i$ is total given the pre-condition that the lower
bound of the input span is less than or equal to its upper bound. 
\end{lemma}
